Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions

### 2015-01-20 HGmodel_draft3.tex
new version

>>>>

\onecolumngrid
{\color{red}
Matti Javanainen has made the text modifications to the manuscript in excellent way. He modified directly the manuscript tex file available in the GitHub and then made a pull request to add a new version of the manuscript into the GitHub repository. In addition, he used latexdiff which can be generated to show the pdf with changes.

After Matti had added his version I looked the changes through and agreed. Then I changed his version to the up-to-date version and made some minor modifications.

All the mentioned files can be found from the GitHub repository
https://github.com/NMRLipids/nmrlipids.blogspot.fi

up-to date manuscript
HGmodel\_draft3.tex

Version Matti uploaded
HGmodel\_draft3\_matti.tex

pdf showing the changes made by matti:
HGmodel\_draft3\_matti\_latexdiff.pdf

I think that this is a very good and convenient way to work collaboratively with the manuscript. If you want you can also make a pull request directly using the up-to-date manuscript file name (HGmodel\_draft3.tex). Then I will accept the pull request, or we will do some discussion before acception. Using latexdiff is very good, but the history will also be saved automatically to the GitHub.

If you find this difficult (as it may be if you are not familiar with GitHub) you can also send your comments and modifications in some other way. However, keep in mind that it is very important to clearly report somehow what you have done. This is to ease my work to handle the input from large amount of contributors.
}
